\documentclass[letterpaper,11pt]{article}

\usepackage[shortlabels]{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage[most]{tcolorbox}

\begin{document}
\title{{\bf Unit 11: Building a Brain} }
\author{Name: TODO}

\date{}
\maketitle

You are designing an egg. It will become a lifeform on a new planet. \textbf{The planet is almost completely covered in water. Small islands made from underwater volcanoes dot the surface. The gravity is stronger on this planet and the biodiversity is lower than on Earth. There is less direct sunlight and fewer living organisms in general}. 
\\\\
Your task is to design the brain and the phenotypes of a successful organism on this new planet, using some of the neuroscience and machine learning principles you have learned so far. Your designed brain and nervous system will be translated into genetic instructions and inserted into an egg that will be sent to the new planet. \textbf{Be as specific as you can so your egg doesn’t become a mutant!}


\section*{Short Answer}
\begin{enumerate}[a)]
\item Insert your design of the brain and the phenotypes of a successful organism on this new planet

\begin{tcolorbox}
TODO: Your answer here.  Feel free to insert images as well
\end{tcolorbox}

\item What do you consider a successful organism?

\begin{tcolorbox}
TODO: Your answer here
\end{tcolorbox}

\item What kinds of traits would support this success; what kinds of organisms on Earth have these traits?

\begin{tcolorbox}
TODO: Your answer here
\end{tcolorbox}

\item What parts of the brain support these traits and what kind of machine learning algorithms might also exhibit these abilities?

\begin{tcolorbox}
TODO: Your answer here
\end{tcolorbox}

\item How might these different traits and abilities need to work together, or connect?

\begin{tcolorbox}
TODO: Your answer here
\end{tcolorbox}
    
\end{enumerate}
\end{document}